SAT Competition 2020\tnoteref{title}

### 2021-01-22 paper/main.tex
moved my sections around
compressed layout for results

\usepackage[utf8x]{inputenc}
\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{multirow,makecell}
\usepackage{float,lscape}
\usepackage[ruled,linesnumbered,vlined]{algorithm2e}

\usepackage{lscape} 
\usepackage[binary-units=true]{siunitx}

\definecolor{gold}{HTML}{FFF3D6}
\definecolor{silver}{HTML}{F3F5F7}
\definecolor{cupper}{HTML}{EAD9D7}
\fboxsep0pt
\newcommand{\firsto}{\colorbox{gold}{\texttt{M1}}}
\newcommand{\firsts}{\colorbox{gold}{\texttt{s1}}}
\newcommand{\firstu}{\colorbox{gold}{\texttt{u1}}}
\newcommand{\firstp}{\colorbox{gold}{\texttt{P1}}}
\newcommand{\secondo}{\colorbox{silver}{\texttt{M2}}}
\newcommand{\seconds}{\colorbox{silver}{\texttt{s2}}}
\newcommand{\secondu}{\colorbox{silver}{\texttt{u2}}}
\newcommand{\secondp}{\colorbox{silver}{\texttt{P2}}}
\newcommand{\thirdo}{\colorbox{cupper}{\texttt{M3}}}
\newcommand{\thirds}{\colorbox{cupper}{\texttt{s3}}}
\newcommand{\thirdu}{\colorbox{cupper}{\texttt{u3}}}
\newcommand{\thirdp}{\colorbox{cupper}{\texttt{P3}}}

@@

\newcommand{\todo}[1]{{\color{purple}Todo: #1}}
\newcommand{\solver}[1]{\texttt{#1}}
\newcommand{\solbert}[1]{\underline{\solver{#1}}}

@@

\begin{table}[t]
\small
\centering
\begin{tabular}{llrr}
\bf Family & \bf Author & \bf Submitted & \bf Selected\\
\hline
\arrayrulecolor{lightgray}
0/1 Integer Programming & \multirow{4}{*}{Riveros} & 6 & 2 \\
Fermat &  & 8 & 5 \\
Schur Coloring &  & 4 & 2 \\
Sum Subset &  & 5 & 2 \\
\hline
Anti-Bandwidth & Biere & 187 & 14 \\
Baseball Lineup & Hickey & 40 & 13 \\
Bit-Vector & Preiner & 393 & 14 \\
Cellular Automata & Chowdhury & 20 & 12 \\
CNF Miter & Manthey & 38 & 7 \\
Coloring & Oostema & 14 & 14 \\
Core-based Generator & Hartung & 20 & 14 \\
Cover & Gacek & 18 & 13 \\
\hline
\multirow{3}{*}{Cryptography} & Paxian & \multirow{3}{*}{106} & \multirow{3}{*}{34} \\
 & Shaw &  &  \\
 & Soos &  &  \\
\hline
Discrete Logarithm & Jingchao & 20 & 7 \\
Edge Matching & Holten & 58 & 7 \\
Flood-It Puzzle & Stiphout & 40 & 0 \\
HGen & Guanfeng & 20 & 13 \\
Hypertree Decomposition & Schidler & 56 & 14 \\
Influence Maximization & Kochemazov & 20 & 14 \\
Lam Discrete Geometry & Nejati & 20 & 9 \\
Polynomial Multiplication & Maoluo & 20 & 8 \\
Station Repacking & Newman & 20 & 12 \\
Stedman Triples & Johnson & 23 & 7 \\
Tensors & Savicky & 20 & 14 \\
Termination Analysis & Yolcu & 12 & 7 \\
Timetable & Djamegni & 20 & 14 \\
Tournament & Heule & 16 & 14 \\
Vlsat & Bouvier & 36 & 14 \\
\arrayrulecolor{black}
\hline
\multicolumn{2}{r}{$\Sigma$} & 1260 & 300
\end{tabular}
\caption{Families and amounts of newly submitted instances}
\label{tab:families}
\end{table}

@@

\begin{table}[t]
\centering
\begin{tabular}{rcccc}
 & SAT & UNSAT & UNKNOWN & $\Sigma$\\
\hline
New Instances & 114 & 78 & 108 & 300 \\
Old Instances & 21 & 57 & 22 & 100\\
\hline
$\Sigma$ & 135 & 135 & 130 & 400
\end{tabular}
\caption{Amount of old and new instances by result}
\label{tab:final}
\end{table}

@@

\begin{table}[h]
  \caption{Number of benchmarks generated by each encoding.}
  \centering
  \begin{tabular}{@{}|l@{\hspace{3pt}}|l|r|r|@{}}
    % &Encoding& SAT & UNSAT\\
    \hline
    \multicolumn{2}{|@{}l|}{Encoding} & SAT & UNSAT\\
    % \midrule
    \hline
    \textbf{H}  & Tree-REX & 15 & 11\\
    \textbf{P}  & PASAR & 14 & 14\\
    \textbf{ME} & Madagascar $\exists$-step & 5 & 10\\
    \textbf{MS} & Madagascar sequential & 66 & 65\\
    % \midrule
    \hline
    && 100 & 100\\
    % \bottomrule
    \hline
  \end{tabular}
  \label{tab:planningBenchmarkDist}
\end{table}

@@

@@

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
1     & 3926.2 & 264 & \solbert{Kissat-sat} \\
(1)   & 4083.1 & 260 & \solver{Kissat} \\
2     & 4179.3 & 253 & \solbert{Relaxed-newTech} \\
3     & 4266.7 & 248 & \solbert{CMS-ccnr-lsids} \\
(3)   & 4278.0 & 250 & \solver{CMS-ccnr} \\
      & 4428.1 & 250 & \solver{CaDiCaL-alluip-trail} \\
      & 4429.6 & 250 & \solver{CaDiCaL-alluip} \\
      & 4436.5 & 245 & \solver{Relaxed} \\
      & 4501.2 & 243 & \solver{CMS-walksat} \\
      & 4554.0 & 243 & \solver{CaDiCaL-trail} \\
      & 4560.0 & 238 & \solver{Kissat-unsat} \\
      & 4607.6 & 246 & \solver{CaDiCaL-sc2020} \\
      & 5157.7 & 216 & \solver{Undominated} \\
      & 5159.6 & 220 & \solver{f2trc-DL} \\
      & 5177.0 & 214 & \solver{PADC-DL} \\              
\end{tabular}
\caption{Main ALL}
\label{tab:mainALL}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
 1    & 2997.4 & 150 & \solbert{Relaxed\_newTech} \\
 2    & 3127.6 & 146 & \solbert{Kissat-sat} \\
 3    & 3263.0 & 144 & \solbert{CMS-ccnr-lsids} \\
(3)   & 3317.4 & 145 & \solver{CMS-ccnr} \\
      & 3355.5 & 143 & \solver{Relaxed} \\
      & 3721.2 & 139 & \solver{CMS-walksat} \\
      & 3830.5 & 134 & \solver{Kissat} \\
      & 3908.5 & 135 & \solver{CaDiCaL-alluip-trail} \\
      & 3909.6 & 135 & \solver{CaDiCaL-alluip} \\
      & 4265.6 & 126 & \solver{CaDiCaL-trail} \\
      & 4368.6 & 130 & \solver{CaDiCaL-sc2020} \\
   & 4804.9 & 114 & \solver{Kissat-unsat} \\
   & 5173.2 & 110 & \solver{Undominated} \\
   & 5244.1 & 107 & \solver{PADC-DL} \\
   & 5264.9 & 110 & \solver{f2trc-DL} \\           
\end{tabular}
\caption{Main SAT}
\label{tab:mainSAT}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline   
1     & 4315.1 & 124 & \solbert{Kissat-unsat} \\
(1)   & 4335.6 & 126 & \solver{Kissat} \\
(1)   & 4724.8 & 118 & \solver{Kissat-sat} \\
 2    & 4842.5 & 117 & \solbert{CaDiCaL-trail} \\
--    & 4846.7 & 116 & \solver{CaDiCaL-sc2020} \\
(2)   & 4947.8 & 115 & \solver{CaDiCaL-alluip-trail} \\
(2)   & 4949.6 & 115 & \solver{CaDiCaL-alluip} \\
 3    & 4991.4 & 110 & \solbert{f2trc-s} \\
(3)   & 5051.4 & 109 & \solver{f2trc} \\
(3)   & 5054.3 & 110 & \solver{f2trc-DL} \\
      & 5069.6 & 109 & \solver{Maple-Mix} \\
      & 5110.0 & 107 & \solver{PADC-DL} \\
      & 5126.9 & 107 & \solver{Maple-Simp} \\
      & 5128.9 & 107 & \solver{MapleCBT-DL-v3} \\
      & 5142.2 & 106 & \solver{Undominated} \\      
\end{tabular}
\caption{Main UNSAT}
\label{tab:mainUNSAT}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline   
 1    & 6406.9 & 80 & \solbert{CaDiCaL-alluip-trail} \\
(1)   & 6409.3 & 80 & \solver{CaDiCaL-alluip} \\
 2    & 6466.9 & 79 & \solbert{CMS-ccnr-lsids} \\
(2)   & 6471.9 & 79 & \solver{CMS-ccnr} \\
(2)   & 6472.9 & 79 & \solver{CMS-walksat} \\
 3    & 6596.4 & 75 & \solbert{Kissat-unsat} \\
      & 6650.1 & 79 & \solver{CaDiCaL-trail} \\
      & 6713.0 & 75 & \solver{Maple-Mix} \\
      & 6746.5 & 75 & \solver{MapleCOMSPS-init} \\
      & 6754.3 & 73 & \solver{Maple-Simp} \\
      & 6773.0 & 73 & \solver{MapleCOMSPS-drup} \\
      & 6773.9 & 73 & \solver{Kissat-sat} \\
      & 6774.2 & 73 & \solver{Kissat} \\
      & 7025.5 & 68 & \solver{upGlucose3.0-PADC} \\
      & 7044.7 & 66 & \solver{Glucose3.0-proofs} \\
\end{tabular}
\caption{Planning (ALL)}
\label{tab:planning}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
 1 & 3316.6 & 283 & \solbert{Painless-MCOMSPS-STR-32} \\
(1)& 3714.7 & 271 & \solver{Painless-MCOMSPS-STR-64} \\
 2 & 3743.4 & 269 & \solbert{Plingeling} \\
 3 & 3985.3 & 260 & \solbert{ManyGlucose-32} \\
   & 4022.7 & 262 & \solver{Painless-Maple-v1} \\
   & 4036.3 & 258 & \solver{ManyGlucose-64} \\
   & 4103.3 & 260 & \solver{Painless-Maple-v2} \\
   & 4433.3 & 243 & \solver{Syrup-Scavel} \\
   & 4903.4 & 225 & \solver{Treengeling} \\
   & 5240.1 & 213 & \solver{abcdsat-p20} \\
\end{tabular}
\caption{Parallel (ALL)}
\label{tab:parallelALL}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
 1 & 2853.7 & 153 & \solbert{Painless-MCOMSPS-STR-32} \\
 2 & 2913.6 & 154 & \solbert{Painless-Maple-v1} \\
(2)& 3082.7 & 151 & \solver{Painless-Maple-v2} \\
-- & 3196.9 & 148 & \solver{Painless-MCOMSPS-STR-64} \\
 3 & 3805.9 & 133 & \solbert{Plingeling} \\
   & 4048.3 & 130 & \solver{ManyGlucose-64} \\
   & 4076.2 & 130 & \solver{ManyGlucose-32} \\
   & 4675.4 & 119 & \solver{Syrup-Scavel} \\
   & 4907.1 & 114 & \solver{Treengeling} \\
   & 6337.5 & \phantom{0}85 & \solver{abcdsat-p20} \\
\end{tabular}
\caption{Parallel (SAT)}
\label{tab:parallelSAT}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
 1 & 3680.8 & 136 & \solbert{Plingeling} \\
 2 & 3779.5 & 130 & \solbert{Painless-MCOMSPS-STR-32} \\
 3 & 3894.3 & 130 & \solbert{ManyGlucose-32} \\
(3)& 4024.2 & 128 & \solver{ManyGlucose-64} \\
   & 4142.8 & 128 & \solver{abcdsat-p20} \\
   & 4191.1 & 124 & \solver{Syrup-Scavel} \\
   & 4232.5 & 123 & \solver{Painless-MCOMSPS-STR-64} \\
   & 4899.8 & 111 & \solver{Treengeling} \\
   & 5123.9 & 109 & \solver{Painless-Maple-v2} \\
   & 5131.9 & 108 & \solver{Painless-Maple-v1} \\
\end{tabular}
\caption{Parallel (UNSAT)}
\label{tab:parallelUNS}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccl}
\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
\hline
 1 & 2603.8 & 299 & \solbert{Mallob-Mono} \\
 2 & 3146.8 & 278 & \solbert{TopoSAT 2} \\
 3 & 4797.6 & 213 & \solbert{Slime} \\
   & 6800.8 & 132 & \solver{Paracooba} \\
   & 7299.0 & 110 & \solver{CTsat} \\
   & 8468.3 & \phantom{0}62 & \solver{Paracooba-March} \\
\end{tabular}
\caption{Cloud (ALL)}
\label{tab:cloud}
\end{table}

\subsection{Planning Track}
% - 86 out of 100 biggest (number of clauses) are planning
% - 109 / 200 in the planning track are not solved by any solver
    % - 186 / 600 in total
% - all 200 above 90\% binary clauses and half have above 99%
The instances of the Planning track are big compared to the rest of the
main track. Using the number of clauses as a metric; out of the $100$ biggest
instances
% of the main-track
$86$ belong to the Planning track. The large size can mainly be attributed to
binary clauses. On average, more than $98$\% of the clauses are binary for
planning instances, where the average for the rest of the instances from the
Main track is below $60$\%.

\includegraphics[width=\textwidth]{stability/ALL_random_smpling_correlations.png}
\includegraphics[width=\textwidth]{stability/fam_leave_one_out_corr.png}

@@

\begin{table}[ht!]
\setlength\tabcolsep{4.5pt}
\smaller
\centering
\begin{tabular}{lllcccc}
\bf Team & \bf Base Solver & \bf Variant / Name & \bf M & \bf U & \bf S & \bf P \\
\hline
\arrayrulecolor{lightgray}

@@

\multirow{2}{*}{Osama, Wijs} 
 & \multirow{2}{*}{\solbert{ParaFROST}} & -- & -- & -- & -- & -- \\
 &  & \solver{CBT} & -- & -- & -- & -- 
\end{tabular}
\caption[Teams and Solvers in the Main Tracks]{Teams and Solvers in the Main Tracks: Column~2 highlights the recent genealogy of submissions and Column~3 displays configuration names as well as names of forks. We partially \solbert{underlined} submission names. Awards in the Main- (M), Planning- (P), Sat- (s), and Unsat- (u) Tracks are indicated by a string TX with $T \in \{M, P, s, u\}$ and $X \in \{1,2,3\}$. }
\label{tab:solvers-main}
\end{table}

@@

\begin{table}[ht]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{llc}
\bf Team & \bf Solver & \bf Score\\
\hline\arrayrulecolor{lightgray}
\stack{Soos, Cai, Devriendt, Gocht, }{Shaw, Meel}~ & \solver{CryptoMiniSat 5} & 3 \\
\hline
\stack{Biere, Fleury}~ & \solver{CaDiCaL 2020} & 1 \\
Chen & \solver{abcdsat-i20} & 1 \\
Manthey & \solver{Riss 7.1.2} & 1 
\end{tabular}
\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track: Score indicates the amount of application categories won with the submission.}
\label{tab:solvers-incremental}
\end{table}

@@

\begin{table}[t]
\smaller
\centering
\begin{tabular}{llc}
\bf Team & \bf Solver & \bf Rank\\
\hline\arrayrulecolor{lightgray}
Schreiber & \solver{mallob-mono} & 1\\
\hline
\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & \solver{TopoSAT2} & 2\\
\hline
Riveros & \solver{Slime} & 3\\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & \solver{Paracooba}, & --\\
& \solver{Paracooba-March} & --\\
\hline
Hartung & \solver{CTSat} & --
\end{tabular}
\caption{Teams and Solvers participating in the cloud track.}
\end{table}

>>>>

\usepackage[utf8x]{inputenc}
\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{multirow,makecell}
\usepackage{float,lscape}
\usepackage[ruled,linesnumbered,vlined]{algorithm2e}
\usepackage{microtype}
\usepackage{lscape} 
\usepackage{tabularx} 
\usepackage{tabulary} 
\usepackage[binary-units=true]{siunitx}

@@

\newcommand{\todo}[1]{{\color{purple}Todo: #1}}
\newcommand{\solver}[1]{\texttt{#1}}
\newcommand{\solbert}[1]{\underline{\solver{#1}}}
\newcommand{\solverine}[1]{\texttt{\textls*[-70]{#1}}}

@@

\begin{table}[t]
\small
\centering
\begin{tabular}{llrr}
\bf Family & \bf Author & \bf Submitted & \bf Selected\\
\hline\arrayrulecolor{lightgray}
0/1 Integer Programming & \multirow{4}{*}{Riveros} & 6 & 2 \\
Fermat &  & 8 & 5 \\
Schur Coloring &  & 4 & 2 \\
Sum Subset &  & 5 & 2 \\
\hline
Anti-Bandwidth & Biere & 187 & 14 \\
Baseball Lineup & Hickey & 40 & 13 \\
Bit-Vector & Preiner & 393 & 14 \\
Cellular Automata & Chowdhury & 20 & 12 \\
CNF Miter & Manthey & 38 & 7 \\
Coloring & Oostema & 14 & 14 \\
Core-based Generator & Hartung & 20 & 14 \\
Cover & Gacek & 18 & 13 \\
\hline
\multirow{3}{*}{Cryptography} & Paxian & \multirow{3}{*}{106} & \multirow{3}{*}{34} \\
 & Shaw &  &  \\
 & Soos &  &  \\
\hline
Discrete Logarithm & Jingchao & 20 & 7 \\
Edge Matching & Holten & 58 & 7 \\
Flood-It Puzzle & Stiphout & 40 & 0 \\
HGen & Guanfeng & 20 & 13 \\
Hypertree Decomposition & Schidler & 56 & 14 \\
Influence Maximization & Kochemazov & 20 & 14 \\
Lam Discrete Geometry & Nejati & 20 & 9 \\
Polynomial Multiplication & Maoluo & 20 & 8 \\
Station Repacking & Newman & 20 & 12 \\
Stedman Triples & Johnson & 23 & 7 \\
Tensors & Savicky & 20 & 14 \\
Termination Analysis & Yolcu & 12 & 7 \\
Timetable & Djamegni & 20 & 14 \\
Tournament & Heule & 16 & 14 \\
Vlsat & Bouvier & 36 & 14 \\
\arrayrulecolor{black}
\hline
\multicolumn{2}{r}{$\Sigma$} & 1260 & 300
\end{tabular}
\caption{Families and amounts of newly submitted instances}
\label{tab:families}
\end{table}

@@

\begin{table}[t]
\centering
\begin{tabular}{rcccc}
 & SAT & UNSAT & UNKNOWN & $\Sigma$\\
\hline\arrayrulecolor{lightgray}
New Instances & 114 & 78 & 108 & 300 \\
Old Instances & 21 & 57 & 22 & 100\\
\hline
$\Sigma$ & 135 & 135 & 130 & 400
\end{tabular}
\caption{Amount of old and new instances by result}
\label{tab:final}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llrr}
\multicolumn{2}{l}{Encoding} & SAT& UNSAT\\
\hline\arrayrulecolor{lightgray}
\textbf{H}  & Tree-REX & 15 & 11\\
\textbf{P}  & PASAR & 14 & 14\\
\textbf{ME} & Madagascar $\exists$-step & 5 & 10\\
\textbf{MS} & Madagascar sequential & 66 & 65\\
\hline
&& 100 & 100\\
\end{tabular}
\label{tab:planningBenchmarkDist}
\caption{Number of benchmarks generated by each encoding.}
\end{table}

@@

% - 86 out of 100 biggest (number of clauses) are planning
% - 109 / 200 in the planning track are not solved by any solver
    % - 186 / 600 in total
% - all 200 above 90\% binary clauses and half have above 99%
The instances of the Planning track are big compared to the rest of the
main track. Using the number of clauses as a metric; out of the $100$ biggest
instances
% of the main-track
$86$ belong to the Planning track. The large size can mainly be attributed to
binary clauses. On average, more than $98$\% of the clauses are binary for
planning instances, where the average for the rest of the instances from the
Main track is below $60$\%.

@@

\begin{table}
\centering\smaller
\setlength\tabcolsep{3pt}
%\begin{tabularx}{\linewidth}{X} \hline \end{tabularx}
\begin{tabularx}{.47\linewidth}{cccX}
\multicolumn{4}{l}{\bf Main Track}\\
\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
\arrayrulecolor{lightgray}\hline
1     & 3926.2 & 264 & \solbert{Kissat-sat} \\
(1)   & 4083.1 & 260 & \solver{Kissat} \\
2     & 4179.3 & 253 & \solbert{Relaxed-newTech} \\
3     & 4266.7 & 248 & \solbert{CMS-ccnr-lsids} \\
(3)   & 4278.0 & 250 & \solver{CMS-ccnr} \\
      & 4428.1 & 250 & \solver{CaDiCaL-alluip-trail} \\
      & 4429.6 & 250 & \solver{CaDiCaL-alluip} \\
      & 4436.5 & 245 & \solver{Relaxed} \\
      & 4501.2 & 243 & \solver{CMS-walksat} \\
      & 4554.0 & 243 & \solver{CaDiCaL-trail}%
%      & 4560.0 & 238 & \solver{Kissat-unsat} \\
%      & 4607.6 & 246 & \solver{CaDiCaL-sc2020} \\
%      & 5157.7 & 216 & \solver{Undominated} \\
%      & 5159.6 & 220 & \solver{f2trc-DL} \\
%      & 5177.0 & 214 & \solver{PADC-DL} \\  
\end{tabularx}\quad%
\begin{tabularx}{.5\linewidth}{cccX}
\multicolumn{4}{l}{\bf Parallel Track}\\
\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
\arrayrulecolor{lightgray}\hline
 1 & 3316.6 & 283 & \solbert{Painless-MCOMSPS-str32} \\
(1)& 3714.7 & 271 & \solver{Painless-MCOMSPS-str64} \\
 2 & 3743.4 & 269 & \solbert{Plingeling} \\
 3 & 3985.3 & 260 & \solbert{ManyGlucose-32} \\
   & 4022.7 & 262 & \solver{Painless-Maple-v1} \\
   & 4036.3 & 258 & \solver{ManyGlucose-64} \\
   & 4103.3 & 260 & \solver{Painless-Maple-v2} \\
   & 4433.3 & 243 & \solver{Syrup-Scavel} \\
   & 4903.4 & 225 & \solver{Treengeling} \\
   & 5240.1 & 213 & \solver{abcdsat-p20} \\
\end{tabularx}
~\\[1em]
\begin{tabularx}{.47\linewidth}{cccX}
\multicolumn{4}{l}{\bf Main Track, Satisfiable Instances}\\
\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
\arrayrulecolor{lightgray}\hline  
 1    & 2997.4 & 150 & \solbert{Relaxed-newTech} \\
 2    & 3127.6 & 146 & \solbert{Kissat-sat} \\
 3    & 3263.0 & 144 & \solbert{CMS-ccnr-lsids} \\
(3)   & 3317.4 & 145 & \solver{CMS-ccnr} \\
      & 3355.5 & 143 & \solver{Relaxed} \\
      & 3721.2 & 139 & \solver{CMS-walksat} \\
      & 3830.5 & 134 & \solver{Kissat} \\
      & 3908.5 & 135 & \solver{CaDiCaL-alluip-trail} \\
      & 3909.6 & 135 & \solver{CaDiCaL-alluip} \\
      & 4265.6 & 126 & \solver{CaDiCaL-trail}%
%      & 4368.6 & 130 & \solver{CaDiCaL-sc2020} \\
%   & 4804.9 & 114 & \solver{Kissat-unsat} \\
%   & 5173.2 & 110 & \solver{Undominated} \\
%   & 5244.1 & 107 & \solver{PADC-DL} \\
%   & 5264.9 & 110 & \solver{f2trc-DL} \\           
\end{tabularx}\quad%
\begin{tabularx}{.5\linewidth}{cccX}
\multicolumn{4}{l}{\bf Parallel Track, Satisfiable Instances}\\
\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
\arrayrulecolor{lightgray}\hline
 1 & 2853.7 & 153 & \solbert{Painless-MCOMSPS-str32} \\
 2 & 2913.6 & 154 & \solbert{Painless-Maple-v1} \\
(2)& 3082.7 & 151 & \solver{Painless-Maple-v2} \\
-- & 3196.9 & 148 & \solver{Painless-MCOMSPS-str64} \\
 3 & 3805.9 & 133 & \solbert{Plingeling} \\
   & 4048.3 & 130 & \solver{ManyGlucose-64} \\
   & 4076.2 & 130 & \solver{ManyGlucose-32} \\
   & 4675.4 & 119 & \solver{Syrup-Scavel} \\
   & 4907.1 & 114 & \solver{Treengeling} \\
   & 6337.5 & \phantom{0}85 & \solver{abcdsat-p20} \\
\end{tabularx}
~\\[1em]
\begin{tabularx}{.47\linewidth}{cccX}
\multicolumn{4}{l}{\bf Main Track, Unsatisfiable Instances}\\
\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
\arrayrulecolor{lightgray}\hline   
1     & 4315.1 & 124 & \solbert{Kissat-unsat} \\
(1)   & 4335.6 & 126 & \solver{Kissat} \\
(1)   & 4724.8 & 118 & \solver{Kissat-sat} \\
 2    & 4842.5 & 117 & \solbert{CaDiCaL-trail} \\
--    & 4846.7 & 116 & \solver{CaDiCaL-sc2020} \\
(2)   & 4947.8 & 115 & \solver{CaDiCaL-alluip-trail} \\
(2)   & 4949.6 & 115 & \solver{CaDiCaL-alluip} \\
 3    & 4991.4 & 110 & \solbert{f2trc-s} \\
(3)   & 5051.4 & 109 & \solver{f2trc} \\
(3)   & 5054.3 & 110 & \solver{f2trc-DL}%
%      & 5069.6 & 109 & \solver{Maple-Mix} \\
%      & 5110.0 & 107 & \solver{PADC-DL} \\
%      & 5126.9 & 107 & \solver{Maple-Simp} \\
%      & 5128.9 & 107 & \solver{MapleCBT-DL-v3} \\
%      & 5142.2 & 106 & \solver{Undominated} \\  
\end{tabularx}\quad%
\begin{tabularx}{.5\linewidth}{cccX}
\multicolumn{4}{l}{\bf Parallel Track, Unsatisfiable Instances}\\
\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
\arrayrulecolor{lightgray}\hline
 1 & 3680.8 & 136 & \solbert{Plingeling} \\
 2 & 3779.5 & 130 & \solbert{Painless-MCOMSPS-str32} \\
 3 & 3894.3 & 130 & \solbert{ManyGlucose-32} \\
(3)& 4024.2 & 128 & \solver{ManyGlucose-64} \\
   & 4142.8 & 128 & \solver{abcdsat-p20} \\
   & 4191.1 & 124 & \solver{Syrup-Scavel} \\
   & 4232.5 & 123 & \solver{Painless-MCOMSPS-str64} \\
   & 4899.8 & 111 & \solver{Treengeling} \\
   & 5123.9 & 109 & \solver{Painless-Maple-v2} \\
   & 5131.9 & 108 & \solver{Painless-Maple-v1}%
\end{tabularx}
~\\[1em]
\begin{tabularx}{.47\linewidth}{cccX}
\multicolumn{4}{l}{\bf Planning Track}\\
\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
\arrayrulecolor{lightgray}\hline   
 1    & 6406.9 & 80 & \solbert{CaDiCaL-alluip-trail} \\
(1)   & 6409.3 & 80 & \solver{CaDiCaL-alluip} \\
 2    & 6466.9 & 79 & \solbert{CMS-ccnr-lsids} \\
(2)   & 6471.9 & 79 & \solver{CMS-ccnr} \\
(2)   & 6472.9 & 79 & \solver{CMS-walksat} \\
 3    & 6596.4 & 75 & \solbert{Kissat-unsat} \\
      & 6650.1 & 79 & \solver{CaDiCaL-trail} \\
      & 6713.0 & 75 & \solver{Maple-Mix} \\
      & 6746.5 & 75 & \solver{MapleCOMSPS-init} \\
      & 6754.3 & 73 & \solver{Maple-Simp}%
%      & 6773.0 & 73 & \solver{MapleCOMSPS-drup} \\
%      & 6773.9 & 73 & \solver{Kissat-sat} \\
%      & 6774.2 & 73 & \solver{Kissat} \\
%      & 7025.5 & 68 & \solver{upGlucose3.0-PADC} \\
%      & 7044.7 & 66 & \solver{Glucose3.0-proofs} \\
\end{tabularx}\quad%
\begin{tabularx}{.5\linewidth}{cccX}
\arrayrulecolor{lightgray}
\multicolumn{4}{l}{\bf Cloud Track}\\
%\hline
\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
\hline
 1 & 2603.8 & 299 & \solbert{Mallob-Mono} \\
 2 & 3146.8 & 278 & \solbert{TopoSAT 2} \\
 3 & 4797.6 & 213 & \solbert{Slime} \\
   & 6800.8 & 132 & \solver{Paracooba} \\
   & 7299.0 & 110 & \solver{CTsat} \\
   & 8468.3 & \phantom{0}62 & \solver{Paracooba-March} \\
\phantom{0} & \phantom{0} & \phantom{0} & \phantom{0}\\
\phantom{0} & \phantom{0} & \phantom{0} & \phantom{0}\\
\phantom{0} & \phantom{0} & \phantom{0} & \phantom{0}\\
\phantom{0} & \phantom{0} & \phantom{0} & \phantom{0}
\end{tabularx}
\caption{Results of Main, Planning, Parallel and Cloud Tracks: Place~(Pl.), Score (PAR-2) and Number of Solved Instances~(\#) per Solver}
\label{tab:cloud}
\end{table}

@@

\begin{table}[h!]
\setlength\tabcolsep{4.5pt}%default: 6pt
%\renewcommand{\arraystretch}{1.03}%default: 1
\smaller
\centering
\begin{tabularx}{\linewidth}{Xllcccc}
\bf Team & \bf Base Solver & \bf Variant / Name & \bf M & \bf U & \bf S & \bf P \\
\hline
\arrayrulecolor{lightgray}

@@

\multirow{2}{*}{Osama, Wijs} 
 & \multirow{2}{*}{\solbert{ParaFROST}} & -- & -- & -- & -- & -- \\
 &  & \solver{CBT} & -- & -- & -- & -- 
\end{tabularx}
\caption[Teams and Solvers in the Main Tracks]{\emph{Teams} and \emph{Solvers} in the Main Tracks. \emph{Base Solver} highlights solver genealogy while \emph{Variant} displays names of configurations and forks. Distinctive names are \solbert{underlined}. The rightmost columns indicate the awards given in the Main (\emph{M}) and Planning track (\emph{P}), and for performance on unsatisfiable (\emph{U}) and satisfiable (\emph{S}) instances.}
\label{tab:solvers-main}
\end{table}

@@

\begin{table}[ht]
%\smaller
\centering
\begin{tabularx}{\linewidth}{lXc}
\bf Team & \bf Solver & \bf Score\\
\hline
Soos, Cai, Devriendt, Gocht, Shaw, Meel & \solver{CryptoMiniSat 5} & 3 \\
\stack{Biere, Fleury}~ & \solver{CaDiCaL 2020} & 1 \\
Chen & \solver{abcdsat-i20} & 1 \\
Manthey & \solver{Riss 7.1.2} & 1 
\end{tabularx}
\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track: Score indicates the amount of application categories won with the submission.}
\label{tab:solvers-incremental}
\end{table}

@@

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{Xlc}
\bf Team & \bf Solver & \bf Rank\\
\hline\arrayrulecolor{lightgray}
Schreiber & \solver{Mallob Mono} & 1\\
Ehlers, Kulczynski, Nowotka, Sieweck & \solver{TopoSAT 2} & 2\\
Riveros & \solver{Slime} & 3\\
\hline
\multirow{2}{*}{Biere, Fazekas, Fleury, Heisinger} & \solver{Paracooba}, & --\\
& \solver{Paracooba-March} & --\\
\hline
Hartung & \solver{CTSat} & --
\end{tabularx}
\caption{Teams and solvers participating in the Cloud track.}
\end{table}
